New seismological constraints on the available parameter space of macroscopic dark matter

### 2016-09-10 LaTeX/Article_Draft_EDITED.tex
Data Complete

The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}. Therefore, we only calculate the energy contained in the modes of frequency less than $16\,\te{Hz}$.

>>>>

The seismometers on the moon have a net useful range of up to $16\,\te{Hz}$ and are sensitive to displacements as small as $0.3\,\text{nm}$ \cite{latham1973lunar}\cite{nakamura1982apollo}. However, they were primarily run in low frequency peaked response mode \cite{eichelman1974apollo}. In this mode, the useful range is limited to $2\te{ Hz}$. Therefore, we only calculate the energy contained in the modes of frequency less than $2\,\te{Hz}$.
